Pyro-Velocity

### 2024-07-15 nbs/about/contributing.qmd
nit(contributing): fix `development`
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

Before proceeding ensure you have deactivated any virtual 
environments created with python-ecosystem tools.
The nix flake integrates with [direnv](https://github.com/direnv/direnv) and provides a
[nix devlopment shell](https://github.com/pinellolab/pyrovelocity/blob/v0.2.0/flake.nix#L185) 
that can be activated with

>>>>

Before proceeding ensure you have deactivated any virtual 
environments created with python-ecosystem tools.
The nix flake integrates with [direnv](https://github.com/direnv/direnv) and provides a
[nix development shell](https://github.com/pinellolab/pyrovelocity/blob/v0.2.0/flake.nix#L185) 
that can be activated with
